---
output: pdf_document
---

## Stat2 -- Chapter 9 part 2 Homework

### Ryan Bruno

```{r setup, echo=FALSE, message=FALSE}
library(tidyverse)

sirds <- read.csv("SIRDS.csv", header = TRUE);
flight <- read.csv("FlightResponse.csv", header = TRUE);
election <- read.csv("Election16.csv", header = TRUE);
levee <- read.csv("LeveeFailures.csv", header = TRUE);

dump <- function(mod) {
    print(summary(mod))
    print(mod$coefficients[2])
    odds <- exp(mod$coefficients[2])
    print(odds)
    print(odds / (1 + odds))
}
```

### 1

##### a

$I = -3.6 + 1.714BirthWeight$

For evey pound increase in BodyWeight the odds of surviale increases by 5.701.

##### b

The birthweight p-value has a value of 0.00262 so it is signicantly different then zero and we can reject the null hypothesis.

```{r one, echo = FALSE, eval = FALSE}
glm(survival ~ birthweight, data = sirds, family = "binomial") %>% summary()

```

### 9.34

##### a

The table below shows that there is a relationship between LatCat and Flight. The increase in probability at each level decreases as LatCat goes from one to four.

```{r nine34a, echo = FALSE, eval = FALSE}
flight <- flight %>%
    mutate(one = ifelse(LatCat == 1, 1, 0),
           two = ifelse(LatCat == 2, 1, 0),
           three = ifelse(LatCat == 3, 1, 0),
           four = ifelse(LatCat == 4, 1, 0))

glm(Flight ~ one, data = flight, family = "binomial") %>% dump()
glm(Flight ~ two, data = flight, family = "binomial") %>% dump()
glm(Flight ~ three, data = flight, family = "binomial") %>% dump()
glm(Flight ~ four, data = flight, family = "binomial") %>% dump()
```

|           |   One   |   two   |  three  |  four   |
|----------:|---------|---------|---------|---------|
| log(odds) | 3.1003  | -1.4124 | -3.1309 | -4.0462 |
| odds      | 22.2046 | 0.2435  | 0.0437  | 0.0174  |
| $\pi$     | 0.9568  | 0.1958  | 0.0418  | 0.0172  |

##### b

Model: $I=4.0518-2.2448LatCat$

It does confirm my suspicion in part a as the $\beta_{1}$ is negative and has a significant p-value.

```{r nine34b, echo = FALSE, eval = FALSE}
glm(Flight ~ LatCat, data = flight, family = "binomial") %>% summary()
```

### 9.36

Model: $I = 11.879 - 0.0001785Income + 0.0663HS - 0.2754BA - 0.2520DemRep$

The most (and only) significant variable is Dem.Rep all others are not significant. HS is least significant.

```{r nine36, echo = FALSE, eval = FALSE}
glm(TrumpWin ~ Income + HS + BA + Dem.Rep, data = election, family = "binomial") %>% summary()
```

### 9.38

##### a

From Income to IncomeTh the $\beta_{1}$ changed by a factor of one thousand. From -0.0001967 to -0.1967. The probability changed from 0.4999 to 0.451

##### b

Odds: 0.8214 or $8,214/10,000$

Meaning we expect that for every thousand dollar increase in income the odds increases by 0.8214

##### c

$(0.7363, 0.9164)$


```{r nine38, echo = FALSE, eval = FALSE}
election %>%
    mutate(IncomeTh = Income / 1000) %>%
    glm(data = ., TrumpWin ~ IncomeTh, family = "binomial") %>%
    dump()


0.8215 + 2.00957524 * exp(0.05582)
0.8215 - 2.00957524 * exp(0.05582)
```

### 9.40

##### a

$H_{0}$: $\beta_{1}=0$

##### b

As ConstrictionFactor goes up the probability of a LeveeFailure does down. We know this due to the negative $\beta_{1}$ value which decrease the log(odds). As log(odds) goes down so does odds and probability.

##### c

$-0.691 \pm 1.989 * 0.346 = (-0.0028, -1.3792)$

```{r nine40, echo = FALSE, eval = FALSE}
glm(data = levee, Failure ~ ConstrictionFactor, family = "binomial") %>%
    dump()
-0.691 + 1.989 * 0.346 
-0.691 - 1.989 * 0.346 
```
