---
output: pdf_document
---

## Stat2 -- Chapter 9 Homework

### Ryan Bruno

```{r setup, echo=FALSE, message=FALSE}
library(tidyverse)

#data <- read.csv("Cars.csv", header = TRUE);
load("ex09-20WlkDog.Rda", verbose=FALSE);
launch = read.csv("LAUNCH.csv", header = TRUE);
```

### 9.4a

Odds: $0.8/0.2 = 4/1$

### 9.6ab

#### a

Probability: $1/4$

#### b

Probability: $5/7$

### 9.8

Exposure: $6/4$

No Exposure: $1/99$

### 9.10


#### a

The midpoint shifts from $2/3$ to $2$.

#### b

The midpoint shifts from $2/3$ to $1 2/3$.

#### c

The slope is now negative.

### 9.20ac

#### a

Logit: $Y = -1.883 + 0.1745 Steps$

Probability: $\pi = e^{-1.883 + 0.1745 Steps} / 1 + e^{-1.883 + 0.1745 Steps}$

#### b

Odds Radtio: 1.19

An increase in 1,000 steps increases the odds of going for walk by 1.19.

#### c

$Y = -1.883 + 0.1745 (4)$

$Y = -1.185$

$\pi = e^{-1.185} / 1 + e^{-1.185}$

$\pi = 0.3057 / 1.3057 = 0.234$

### Launch Problem

#### a

Explanatory: Temperature

Response: Success

#### b

Looking at the plot below it is evident that success is related to temperature.

```{r launch1, fig.height = 3, fig.width = 4, echo = FALSE}

ggplot(launch, aes(x = Temperature, y = Success)) +
   geom_point()

```

#### c

Plot with regression line.

```{r launch2, echo = FALSE, eval = FALSE}
summary(lm(Success ~ Temperature, data = launch))
```
```{r launch3, fig.height = 3, fig.width = 4, echo = FALSE}

ggplot(launch, aes(x = Temperature, y = Success)) +
   geom_abline(slope = 0.03738, intercept = -1.90476) +
   geom_point()

```

#### d

Logit: $Y = -15.04 + 0.232 Temperature$

#### e 

31: $Y = -15.04 + 0.232 (31)$

$Y = -7.848$

$\pi = 0.00039 / 1.00039$

50: $Y = -15.04 + 0.232 (50)$

$Y = -3.44$

$\pi = 0.032 / 1.032$

75: $Y = -15.04 + 0.232 (75)$

$Y = 2.36$

$\pi = 10.59 / 11.59$

#### f


$ln(odds) = -15.04 + 0.232 (59)$
$odds = 0.2587 or about 1/4$

This means with 5 trials at 59 degrees about one of them will be a success and 4 will not.
