\documentclass{beamer}

\usepackage[utf8]{inputenc}
\usepackage[final]{pdfpages}

%\usetheme{Default}
%\usecolortheme{beetle}

\setbeamercolor{background canvas}{bg=black}
\setbeamercolor{block title}{bg=white}
\setbeamercolor{fine separation line}{}
\setbeamercolor{frametitle}{fg=white}
\setbeamercolor{normal text}{bg=black,fg=white}
\setbeamercolor{title}{fg=white}
\setbeamercolor{titlelike}{fg=white}

%Information to be included in the title page:
\title{Memory Efficience and Conflict-free Replicated Data Types}
\author{Ryan Bruno \and Dr. Armstrong}
\date{}


\begin{document}

\frame{\titlepage}

\begin{frame}
\frametitle{Problem Description}
Conflict-free Replicated Data Types (CRDTs) use extra metadata to allow for concurrent modifications of data without consensus. How can we reduce the this overhead?
\end{frame}

\begin{frame}
\frametitle{Primary Objective}
To measure the memory reduction of using garbage collection in combination with an OR-Set while keeping the properties of a Conflict-free Replicated Data Type. Limited to 1.5 person weeks over 12 weeks.
\end{frame}

\begin{frame}
\frametitle{Solution Description}

Environment:

\begin{itemize}
\item Must have $> 2$ nodes.
\item Connected via artifical network.
\item Ability to enduce network delays.
\end{itemize}

Software:

\begin{itemize}
\item Node software
\item Administrator software
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Hypothesis}
The sum of the total data set size of each node will be significantly less while using garbage collection then without.
\end{frame}

\end{document}
