---
output: pdf_document
---

## Stat2 -- Chapter 10 Homework

### Ryan Bruno

```{r setup, echo=FALSE, message=FALSE}
library(tidyverse)

```

### 10.2

##### a

--

*Female:*

Probability: 0.44

Odds: $Odds=\pi/(1+\pi)=0.44/(1+0.44)=0.44/1.44=306/1000$

*Male:*

Probability: 0.18

Odds: $Odds=\pi/(1+\pi)=0.18/(1+0.18)=0.18/1.18=153/1000$

##### b

--

\<Odds for Female\>/\<Odds for Male\> = $0.306/0.153 = 2$

#### c

--

The answer from part (b) is different from the ratio given in the problem because they use different models. The one from the problem adds Backpack wight and BodyWeight.

### 10.4

We want a model with $\beta_{0}$, X, and Group with no interaction term because of the parallel three-line relation relationship shown. This is all set to Log(odds) of yes.

Model: $log(odds) = \beta_{0}+\beta_{1}X+\beta_{2}Group\_1+\beta_{3}Group\_2$


### 10.10

Model: $log(odds) = \beta_{0}+\beta_{1}X+\beta_{2}A+\beta_{3}XA$

## 10.12b

Yes because a model with $\log(Acceptance) = \beta_{0} + \beta_{1} GPA + \beta_{2}MCAT + \beta_{3}Sex$ fits to $\beta_{3}$ begin -1.258 while the model $\log(Acceptance) = \beta_{0} + \beta_{1} GPA + \beta_{2}MCAT$ has an almost identical $\beta_{2}$ but a changed $\beta_{1}$.

```{r ten12CSV, echo=FALSE, eval=TRUE}
medgpa <- read.csv("MedGPA.csv", header = TRUE)
```
```{r ten12MODEL, echo=FALSE, eval=FALSE}
glm(Acceptance ~ GPA + MCAT + Sex, data = medgpa, family = "binomial") %>% summary()
glm(Acceptance ~ GPA + MCAT, data = medgpa, family = "binomial") %>% summary()
#glm(Acceptance ~ GPA + Sex, data = medgpa, family = "binomial") %>% summary()
```

## 10.14

The output for the fitted model shows that when Sex\_F is 1 (when the applicant is Female) they are more likely to be accepted by 1.066 log(odds).

## 10.18

##### b

--

Reduced: $I = \beta_{0} + \beta_{1} DilateDiff$

Deviance test: 113.70

Full: $I = \beta_{0} + \beta_{1} DilateDiff + \beta_{2} Sex\_M$

Deviance test: 106.38

```{r ten18CSV, echo=FALSE, eval=FALSE}
eyes <- read.csv("Eyes.csv", header = TRUE)

eyes <- eyes %>%
    mutate(Sex_M = ifelse(Sex == "M", 1, 0)) %>%
    mutate(Sex_F = ifelse(Sex == "F", 1, 0)) %>%
    mutate(DilDif_M = DilateDiff * Sex_M) %>%
    mutate(DilDif_F = DilateDiff * Sex_F)

#glm(Gay ~ DilDif_M + DilDif_F, data = eyes, family = "binomial") %>% summary()
glm(Gay ~ DilateDiff, data = eyes, family = "binomial") %>% summary()
glm(Gay ~ DilateDiff + Sex, data = eyes, family = "binomial") %>% summary()
```

## 10.22

##### b

--

Reduced: $I = \beta_{0} + \beta_{1} MCAT$

Deviance test: 64.697

Full: $I = \beta_{0} + \beta_{1} MCAT + \beta_{2} Sex\_M$

Deviance test: 67.711

```{r ten22CSV, echo=FALSE, eval=FALSE}
#glm(Gay ~ DilDif_M + DilDif_F, data = eyes, family = "binomial") %>% summary()
glm(Acceptance ~ MCAT, data = medgpa, family = "binomial") %>% summary()
glm(Acceptance ~ MCAT + Sex, data = medgpa, family = "binomial") %>% summary()
```

[//]: <> (MedGPA)

## 10.34

##### a

--

Model: $I = -0.22597 - 0.49708Seed + 1.52755Izzo$

```{r ten34CSV, echo=FALSE, eval=FALSE}
izzo <- read.csv("FinalFourIzzo17.csv", header = TRUE)
glm(Final4 ~ Seed + Izzo, data = izzo, family = "binomial") %>% summary()
```

##### b

--

Yes because $\beta_{2}$ is large and the p-value is small.
