---
title: "Ryan Bruno"
author: "Homework #2 - Stat2 - ex01.48"
output: html_document
---

```{r setup, echo=FALSE}
library(ggplot2)
library(dplyr)

load("ex01-48MetRate.Rda")

reg_1 <- lm(data$Mrate~data$BodySize)
reg_2 <- lm(data$LogMrate~data$LogBodySize)

data$predicted_1 <- predict(reg_1, data.frame(data$BodySize))
data$predicted_2 <- predict(reg_2, data.frame(data$LogBodySize))

data <- data %>%
  mutate(Residual_Direct = predicted_1 - Mrate)


data <- data %>%
  mutate(Residual_Log = predicted_2 - LogMrate)

```

## Part A

There is a problem when comparing BodySize and Mrate directly using a linear model (shown below). While it does appear to be linear it's spread is not uniform. This is shown when comparing BodySize to residual (also shown below).

```{r,fig.height=3, fig.width=3, fig.show="hold", echo=FALSE}

ggplot(data, mapping = aes(x = BodySize, y = Mrate)) + 
    geom_point()

ggplot(data, mapping = aes(x = BodySize, y = Residual_Direct)) + 
    geom_point()
```

However, if we try to use either LogBodySize (on the left) or LogMrate (on the right) alone we do not end up with a linear graph.

```{r,fig.height=3, fig.width=3, fig.show="hold", echo=FALSE}

ggplot(data, mapping = aes(x = LogBodySize, y = Mrate)) + 
    geom_point()

ggplot(data, mapping = aes(x = BodySize, y = LogMrate)) + 
    geom_point()
```

The solution is shown when we plot LogBodySize against LogMrate. The resulting model is roughly linear and shows a uniform speard.

```{r,fig.height=3, fig.width=3, fig.show="hold", echo=FALSE}

ggplot(data, mapping = aes(x = LogBodySize, y = LogMrate)) + 
    geom_point()

ggplot(data, mapping = aes(x = LogBodySize, y = Residual_Log)) + 
    geom_point()

```

Final model: **LogMrate = 1.3066 + (0.9164 * LogBodySize)**

## Part B
Below is the work for predicting a caterpillar with a body size of 1 gram:

| Step                            | Work                     |
|---------------------------------|--------------------------|
| First take the log of BodySize  | log(1) = 0               |
| Then multiply                   | 0 * 0.9164 = 0           |
| Then add                        | 0 + 1.3066 = 1.3066      |
| Lastly raise to the power of 10 | 10 ^ 1.3066 = 20.26      |
