---
title: "Ryan Bruno"
author: "Homework #8 - Stat2 - ex03.8 ex03.12"
output: pdf_document
---

```{r setup, echo=FALSE}
library(ggplot2)
library(dplyr)

#load("Caterpillars.rda", verbose = TRUE)
#ex0358Caterp %>% glimpse()
```

# EX03.8:

### Part A:

True. Every predictors added to a model will always increase the $R^{2}$ of the model but may decrease the adjusted $R^{2}$.

### Part B:

True. Building off the previous question when we have a model using $X_{1}$ that has a very high $R^{2}$ and then add $X_{2}$ to the model, no matter how good $X_{2}$'s $R^{2}$ is the resulting model will have a higher $R^{2}$ then the initial $R^{2}$.

# EX03.12

### Part A:

Model -> $Mrate = \beta_{0} + \beta_{1} BodySize +  \beta_{2} I_{fg} + \beta_{3} (I_{fg} BodySize); I_{fg} = 1$ for free growth only.

### Part B:

Model -> $Mrate = \beta_{0} + \beta_{1} BodySize +  \beta_{2} I_{fg} ; I_{fg} = 1$ for free growth only.


### Part C:

Full Model -> $Mrate = \beta_{0} + \beta_{1} BodySize +  \beta_{2} I_{fg} + \beta_{3} (I_{fg} BodySize)$

Reduced Models:

$Mrate = \beta_{0} + \beta_{2} I_{fg}$

$Mrate = \beta_{0} + \beta_{1} BodySize$

$Mrate = \beta_{0} + \beta_{3} (I_{fg} BodySize)$

```{r model1, echo=FALSE}
#model_1 <- lm(ex0324LewyB2$MMSE~ex0324LewyB2$APC)
#summary(model_1)
```
