\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{multicol}
\usepackage[margin={1.25in,1.25in}]{geometry}
\usepackage{titlesec}
\usepackage{titling}
\usepackage{graphicx}

\usepackage{parskip}

\title{Assignment One}
\author{Ryan Bruno}
\date{\today}

\renewcommand{\maketitle}{
    \textbf{\thetitle} \\
    By: \theauthor \\
    \thedate
}

\begin{document}

\maketitle

\section*{Part A}

If I had the resources I would build a massively multiplayer online (mmo) warship battle game.
Players can grind for resources or battle and loot other players.
Navigating the sea can be done with a top-down view but in battle the guns, missiles, and other weapons are aimed in 3D as if your view is the ships.
The game will encourage players to team up, capture important locations, and make in game money off of them.

\section*{Part B}

Going along with the same theme of part a, I can make a single player, top-down warship game set in an enclosed region of water.
You are the main character controlling a boat.
In the same region are enemy bot warships.
The objective is to either avoid detection and pass from one end of the map to another or to fight your way through.

The most important part about the feel of the game will be the ocean with a few animated waves crashing.
Occasionally there will also be landmasses to break up the landscape and hinder visibility.
The ships will also play a lot into the theme of the game.
The enemy ships will be based on current and future military warships while the main character's appear as if has been put together from other salvaged ships.



\end{document}
