---
title: "Ryan Bruno"
author: "Homework #7 - Stat2 - ex03.24"
output: pdf_document
---

```{r setup, echo=FALSE}
library(ggplot2)
library(dplyr)

load("ex0324LewyB2.rda", verbose = FALSE)
```

# Part A:
```{r plot, echo=FALSE}
ggplot(ex0324LewyB2, aes(x = APC, y = MMSE, color = Type)) + 
    geom_point()
```

By looking at the plot above we can see there is a slight difference in slope and intercept between those with type DLB and those with type DLB/AD.

# Part B:
```{r model1, echo=FALSE}
model_1 <- lm(ex0324LewyB2$MMSE~ex0324LewyB2$APC)
#summary(model_1)
```

Model: $MMSE = -1.4214 + 1.7462APC$

Test:

$H_{0}: \beta = 0$
F-Value = 15.74
P-Value = 0.0003208

There is a linear relationship between these two variables because of the low p-value we can reject $H_{0}$

# Part C:
```{r model2, echo=FALSE}
data2 <- ex0324LewyB2 %>%
    filter(Type == "DLB")
model_2 <- lm(data2$MMSE~data2$APC)
data3 <- ex0324LewyB2 %>%
    filter(Type == "DLB/AD")
model_3 <- lm(data3$MMSE~data3$APC)

#summary(model_2)
#summary(model_3)
```

Fitted Equation for Type **DLB**:

Model: $MMSE = -0.5846 + 2.3176APC$

Fitted Equation for Type **DLB/AD**:

Model: $MMSE = -2.4359 + 1.3444APC$

Combined Equation:

$MMSE = -2.4359 + 1.3444APC + 1.8513I + 0.9732(I)(APC)$

I => (DLB = 1) (DLB/AD  = 0)
