\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{multicol}
\usepackage[margin={.95in,.75in}]{geometry}
\usepackage{titlesec}
\usepackage{titling}
\usepackage{xcolor}

\usepackage[T1]{fontenc}
\usepackage[scale=0.95]{opensans}
\usepackage{merriweather}

\usepackage{parskip}

\pagenumbering{gobble}
\setlength{\textwidth}{9in}
\setlength{\parindent}{0in}
\hyphenpenalty=10000
\setlength{\columnsep}{.5in}
\definecolor{Strong-Blue}{RGB}{32, 131, 199}
\definecolor{Dark-Grey}{RGB}{102, 102, 102}
\title{Resume}
\author{Ryan Bruno}
\date{\today}

\renewcommand{\maketitle}{\Huge\textbf{\theauthor}}

\titleformat {\section} % command
[display] % shape
{\bfseries\color{Strong-Blue}} % format
{\thesection} % label
{0.5ex} % sep
{\vspace{1ex}} % before-code
[\vspace{.5ex}] % after-code

\newenvironment{heading} {
    \bfseries
    \normalsize
    \color{black}
    \setlength{\parskip}{1em}
    \renewcommand{\familydefault}{merriweather}
} {\par}
\newenvironment{subtext} {
    \footnotesize
    \color{Dark-Grey}
    \setlength{\parskip}{0.75em}
    \renewcommand{\familydefault}{opensans}
} {\par}

\newenvironment{ntext} {
    \small
    \color{Dark-Grey}
    \setlength{\parskip}{0.75em}
    \renewcommand{\familydefault}{merriweather}
} {\par}

\begin{document}

\begin{multicols}{2}
\maketitle

    {
        \footnotesize
        \renewcommand{\familydefault}{opensans}
        Current Computer Science student looking for a summer internship before my Senior year that will further develop my programming expertise, as I contribute to your firm’s mission and objectives.

    }

\columnbreak
\section*{}

    {
        \footnotesize
        \renewcommand{\familydefault}{opensans}
        Github/RyanBruno \\*
        \textbf{(215) 385-4920} \\*
        \textbf{RB4359@ship.edu}

    }
\end{multicols}

\begin{multicols}{2}

\section*{EDUCATION}

    \begin{heading}
        Shippensburg University \mdseries — \textit{Computer Science Major}
    \end{heading}

    \begin{subtext}
        Auguest 2017-PRESENT
    \end{subtext}

    \begin{ntext}
        4 Semesters Completed \textbf{(3.5/4.0 GPA).}
    \end{ntext}

\section*{CORSE WORK}

    \begin{heading}
        Artificial Intelligence
    \end{heading}

    \begin{subtext}
        August 2019 - PRESENT
    \end{subtext}

    \begin{ntext}
        Overview of artificial intelligence with an emphasis on basic tools of AI, search and knowledge representation, and their application to a variety of AI problems.
    \end{ntext}

    \begin{heading}
        Design and Analysis of Algorithms
    \end{heading}

    \begin{subtext}
        Spring 2018
    \end{subtext}

    \begin{ntext}
        Study of the theoretical foundations for the analysis of algorithms and the ramifications of design strategies on efficiency.
    \end{ntext}

    \begin{heading}
        Design Patterns
    \end{heading}

    \begin{subtext}
        Fall 2018
    \end{subtext}

    \begin{ntext}
        An advanced study of the concepts of object-oriented programming, with an emphasis on applying those concepts to software development.
    \end{ntext}

    \begin{heading}
       Computer Organization
    \end{heading}

    \begin{subtext}
        Spring 2018
    \end{subtext}

    \begin{ntext}
        Introduced organization and architecture of computer systems from the standard von Neumann model to more recent architectural concepts.
    \end{ntext}

    \begin{heading}
        Computer Science II
    \end{heading}

    \begin{subtext}
        Fall 2017
    \end{subtext}

    \begin{ntext}
        The application of techniques such as pointers, structures, unions as well as various abstract data types to create advanced programs and solutions.
    \end{ntext}

\columnbreak
\section*{SKILLS}

    \begin{ntext}
        Proficient in: Java, C/C++, \\
        Javascript, and Node.js

        Knowledge of cloud \\
        technologies, Docker, AWS

        Experience in NoSQL database \\
        management

        Cisco router and switch \\
        configuration including IPv6
    \end{ntext}

\section*{AWARDS}
    \begin{ntext}

        \textbf{3 Semester Dean's List} at \\
        Shippensburg University for \\
        having a 3.5 GPA or higher.

        \textbf{2 PSAC Scholar-Athlete} for \\
        maintaining a 3.25 cumulative \\
        GPA while in season.

    \end{ntext}
\section*{ACTIVITES}
    \begin{ntext}

        Shippensburg University \\
        Football Player.

        Hatboro-Horsham High \\
        School Varsity Football Player.
    \end{ntext}

\end{multicols}
\end{document}
