---
title: "Ryan Bruno"
author: "Homework #5 - Stat2 - ex02.36"
output: pdf_document
---

```{r setup, echo=FALSE}
library(ggplot2)
library(dplyr)

load("ex02-36ChldSpk.Rda")

```

# Problem 2.36:

## Part a:

I would expect there to be a relationship between Gesell score and speaking age because both are measurements of cognition in children. For the Gesell score, a higher number is better while for speaking age a lower score is better therefore the relationship should be negative.

## Part b:

```{r, fig.height=4, fig.width=4, echo=FALSE}

ggplot(data, aes(x = Gesell, y = Age)) +
    geom_point() + 
    geom_smooth(method='lm', formula= y~x, se= FALSE)

```

Based on the plot there does appear to be evidence that Gesell scores can predict speaking age, however, it also shows the plot has a large amount of influential points.

## Part c:

$r^{2}$ = 0.4099

$H_{0}: \beta = 0$

t = $\displaystyle \frac{sqrt(r^{2} * 19)}{sqrt(1 - r^{2})} = 3.633$

OR

$\beta = -0.3638$

SE = 0.1001

$t = \displaystyle \frac{\beta}{SE} = -3.633$

P-Value = 0.00177

Since our p-value is small we can reject our null hypothesis and state the relationship between Gesell scores and speaking age is significant.

## Part d:

The observation with the largest residual is child number 19. With a Gesell score of 121 we expect the child's speaking age to be 4.4 months but observed 17 months (a residual of 12.6).

# Problem 2.40:

## Part a:

To consutruct a confidence interval we start by getting a y-hat for the list price $y = \beta_{0} + \beta_{1}x = 292,774$.

$C.I. = y \pm t * SE_{\mu} = (281,833-283,716)$

## Part b:

Prediction Interval:

$P.I. = y \pm t * SE_{y} = (269,537-296,011)$

## Part c:

The confidence interval states with a 90% confidence we expect the mean sales price for the given list price of \$300,000 to be between \$281,833 and \$283,716. The Prediction interval says if there is a single house with a list price of \$300,000 we expect with a 90% confidence to be between \$269,537 and \$296,011.


```{r, echo=FALSE}

#summary(lm(data$Age~data$Gesell))$r.squared
#summary(lm(data$Age~data$Gesell))
#load("ex02-40Grinnell.Rda")
#model <- lm(SalePrice~ListPrice, data = data)
#summary(model)
#predict(model, data.frame(ListPrice = c(300000)), interval="confidence", level=0.90)
#predict(model, data.frame(ListPrice = c(300000)), interval="predict", level=0.90)


```
