---
output: pdf_document
---

## Stat2 -- Chapter 3 Review

### Ryan Bruno

```{r setup, echo=FALSE}

#title: "Ryan Bruno"
#author: "Chapter 3 Review - Stat2"
library(ggplot2)
library(dplyr)

load("Pollster08.rda",  verbose = FALSE)
data <- ex0343Poll08
```

### Question 1

The trend of the below scatter plot seems to be corralated upwards after about 10 days after the Democratic Convention.

```{r one, echo=FALSE, fig.height=3, fig.width=4}
ggplot(data, aes(x = Days, y = Margin)) +
    geom_point() # Describe trend
```

### Question 2

Model: $Margin = 4.47796 - 0.604426 Days + 0.021129 Days^{2}$

$r^{2} = 0.3495$

SSE = 899.24

```{r two, echo=FALSE, eval=FALSE}
data <- data %>%
    mutate(DaysSqred = Days * Days)
model_1 <- lm(Margin~Days+DaysSqred, data=data)
summary(model_1) # Model R^2 SSE
sum(model_1$residuals**2)
```

### Question 3

Model: $Margin = -0.31282 + 0.12222 Days + 0.6364 Charlie$

$r^{2} = 0.1458$

SSE = 1180.747

```{r three, echo=FALSE, eval=FALSE}
model_2 <- lm(Margin~Days+Charlie, data=data)
summary(model_2) # Model R^2 SSE
sum(model_2$residuals**2)
```

### Question 4

Model: $Margin = 0.73533 + 0.001412 Days + 3.18718 Meltdown$

$r^{2} = 0.1900$

SSE = 1119.66

```{r four, echo=FALSE, eval=FALSE}
model_3 <- lm(Margin~Days+Meltdown, data=data)
summary(model_3) # Model R^2 SSE
sum(model_3$residuals**2)
```

### Question 5

Looking at the $R^{2}$ and SSE values the model in question 2 is a better model to explain the data then the model in question 4. This tells us that a quadratic model of just days is better then a linear model with days and meltdown.
